### 2022-08-19 manuscript.Rmd
Add text for TFR results

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive")
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

# Read channel locations
channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
```

@@

```{r, clusters, include=TRUE, fig.height=8}
# Read results of cluster-based permutation tests for ERPs
read_csv(here(output_dir, "clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

```{r, tfr, fig.height=12, include=TRUE}
# Read results of cluster-based permutation tests for TFR
read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters

```{r, fig2a, fig.height=10, include=TRUE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations, tmin = -0.4, tmax = 1.4, tstep = 0.2)

@@

>>>>

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline_tmin = -0.2,
    baseline_tmax = 0.0,
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_baseline_tmin = -0.45,
    tfr_baseline_tmax = -0.05,
    tfr_baseline_mode = "percent",
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive")
    ),
    perm_tmin = 0.0,
    perm_tmax = 1.0,
    n_jobs = 1
  )
}

@@

# Read channel locations
channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))

# Read results of cluster-based permutation tests for ERPs
clusters <- read_csv(here(output_dir, "clusters.csv"))

# Read results of cluster-based permutation tests for TFR
tfr_clusters <- read_csv(here(output_dir, "tfr_clusters.csv"))
```

@@

## Event-Related Power

In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`.
These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
Both clusters had a negative sign, started around 600 ms after object onset and continued all the way until the end of the analyzed period at 1,400 ms.
They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz at parietal channels.
Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.

```{r, fig2, fig.height=10, include=TRUE, eval=FALSE}
# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)

@@

```{r, figclusters, include=TRUE, fig.height=8}
# Read results of cluster-based permutation tests for ERPs
read_csv(here(output_dir, "clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

```{r, figtfrclusters, fig.height=12, include=TRUE}
# Read results of cluster-based permutation tests for TFR
read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters
